### 2013-11-14 research/paper/results/results-2.3.tex
Added m_star part

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced. However, when the sinusoidal forcing function in Eq.\ref{equationofmotion} which cater for the vortex shedding was disregarded, the reduction in power could not be observed Fig.\ref{fig:m_star_collapsed}(b). An influence of vortex shedding on power is present. This maybe due to the reduction in inertia as the mass ratio is decreased.

At \reynoldsnumber=22300 two major phenomena could be observed. The maximum of the mean power tend to increase  as the $m^*$ was decreased while keeping the $U^*$ constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same \hilight{phenomenon} occurring in both cases whereby the velocity signal tend to move towards a square from a sinusoidal signal. The displacement signal tend to become more triangular. the reason behind the increase in power while reducing mass ratio is due to the fact that the inertia of the system becomes low. Therefore the body accelerate faster and attains higher velocity quickly. Therefore the time period where the body sustains high velocity increases which will lead to an increase in time period where the body in influenced by the higher forcing, which leads to a higher power output. As for the case to where the mean power increases with increasing $U^*$ for a given low mass ratio, the exploration tend to be similar where the only difference being that the at high $U^*$ the period of oscillation tend to increase therefore the body sustains higher velocities for a longer time leading to a higher power output.

>>>>

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant for $m^*<30$ in the low \reynoldsnumber case. However, at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range. However, when the sinusoidal forcing function in Eq.\ref{equationofmotion} which cater for the vortex shedding was disregarded, the reduction in power could not be observed Fig.\ref{fig:m_star_collapsed}(b). The suppression of galloping response at low $m^*$ due to the presence of vortex shedding has previously been observed by \cite{Joly2012}. This is a non-linear interaction between the forcing that drives the galloping excitation and the forcing as a result of vortex shedding. The forcing associated with vortex  shedding is significantly larger and at a higher frequency than the forcing that drives galloping. Systems with low $m^*$ do not have enough inertia to fully sustain the galloping excitation over the longer period.

At \reynoldsnumber=22300 power output started to increase for cases with $m^*<50$. The overall mean power tend to increase  as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios presented in Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same phenomenon occurring in both cases whereby the velocity signal tend to shift from a sinusoidal signal towards a square wave. The corresponding displacement signal tend to become more like a triangular wave. When the inertia of the system reduces, the body can accelerate faster thus attaining higher velocities more rapidly and spend a higher proportion of the period at a high velocity. Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping. However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $6 ^0$ degrees which correspond to a transverse velocity of $\frac{\dot{y}}{U}=$. Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output. For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at ??? being more dominant on the overall mass of the system when m* is reduced.
